Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-09-27 paper/main.tex
small fix

The number of valid mutants is usually
slightly smaller for Comby, but Comby actually produces a larger mean
(but not median) number of mutants for Rust, due to one project where
Comby produces a much larger number of valid mutants.  The small gain
in valid mutants for Regexp is partly due to Regexp (unfortunately)
mutating some comments, and partly due to a reported, but not yet
fixed, bug in Comby's handling of an operator swapping items in
literal lists.  As discussed
below, mutation scores and mutant equivalence rates are similar for
both modes.

>>>>

The number of valid mutants is usually
slightly smaller for Comby, but Comby actually produces a larger mean
(but not median) number of mutants for Rust, due to one project where
Comby produces a much larger number of valid mutants.  The small gain
in valid mutants for Regexp is partly due to Regexp (unfortunately)
mutating some comments, and partly due to a reported, but not yet
fixed, bug in the Python front-end to Comby, affecting an operator
that swaps literal list items.  As discussed
below, mutation scores and mutant equivalence rates are very similar for
both modes; mean mutation scores differed by at most 0.3, and project
scores by more only for Rust.
